Exploratory Plots

### 2020-09-13 exploratory/2020/sub3_fit_subsets.Rmd
Write rule to merge gap counts
More runtime plots

---
title: "Exploratory Plots"
date: "Aug. 2020"
output: 
  github_document:
    html_preview: false
---

@@

## Runtime
```{r runtime_ref_size}
runtime <- full_join(
  read_tsv(here('subworkflows/3_fit_sample_subset/results/benchmarks.tsv')),
  read_tsv(here('subworkflows/3_fit_sample_subset/results/input_sizes.tsv'))
  )
runtime %>% ggplot(aes(x=num_ref_seqs, y=s, color=dataset)) +
  geom_point(alpha = 0.5) +
  scale_color_manual(values = dataset_colors) +
  labs(title = 'Runtime over reference size',
       x = '# sequences in reference',
       y = 'seconds')
```

```{r runtime_sample_size}
runtime %>% ggplot(aes(x=num_sample_seqs, y=s, color=dataset)) +
  geom_point(alpha = 0.5) +
  scale_color_manual(values = dataset_colors) +
  labs(title = 'Runtime over sample size',
       x = '# sequences in sample',
       y = 'seconds')
```

>>>>

---
title: "Exploratory Plots"
date: "Sept. 2020"
output: 
  github_document:
    html_preview: false
---

@@

## Runtime
```{r runtime_ref_seqs}
runtime <- full_join(
  read_tsv(here('subworkflows/3_fit_sample_subset/results/benchmarks.tsv')),
  read_tsv(here('subworkflows/3_fit_sample_subset/results/input_sizes.tsv'))
  ) %>% 
  full_join(read_tsv(here('subworkflows/3_fit_sample_subset/results/gap_counts.tsv'))) %>% 
  mutate(num_total_seqs = num_ref_seqs + num_sample_seqs,
         gaps_frac = n_gaps / total_chars)
runtime %>% ggplot(aes(x=num_ref_seqs, y=s, color=dataset)) +
  geom_point(alpha = 0.3) +
  facet_grid(method ~ ref_weight) +
  scale_color_manual(values = dataset_colors) +
  labs(title = 'Runtime over reference size',
       x = '# sequences in reference',
       y = 'seconds')
```

```{r runtime_total_seqs}
runtime %>% 
  ggplot(aes(x=num_total_seqs, y=s, color=dataset)) +
  geom_point(alpha = 0.5) +
  facet_grid(method ~ ref_weight) +
  scale_color_manual(values = dataset_colors) +
  xlim(0, 300000) +
  labs(title = 'Runtime over sample + reference size',
       x = '# sequences total',
       y = 'seconds')
```

```{r runtime_gaps}
runtime %>% 
  ggplot(aes(x=n_gaps, y=s, color=dataset)) +
  geom_point(alpha = 0.5) +
  facet_grid(method ~ ref_weight) +
  scale_color_manual(values = dataset_colors) +
  labs(title = 'Runtime over number of gaps',
       x = '# gaps',
       y = 'seconds')
```

```{r runtime_numotus}
runtime %>% full_join(sensspec_fit) %>% 
  ggplot(aes(x=numotus, y=s, color=dataset, shape = ref_weight)) +
  geom_point(alpha = 0.5) +
  facet_grid(method ~ ref_weight) +
  scale_color_manual(values = dataset_colors) +
  labs(title = 'Runtime over number of OTUs',
       x = '# OTUs',
       y = 'seconds')
```
